\documentclass[11pt,letterpaper]{article}
\usepackage[margin=1in]{geometry}
\usepackage{setspace}
\usepackage{enumitem}
\usepackage{array}
\usepackage{booktabs}
\usepackage{tabularx}
\usepackage{graphicx}
\usepackage{titlesec}
\usepackage{fancyhdr}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{lmodern}

\setstretch{1.03}
\pagestyle{empty}
\setlength{\parindent}{15pt}
\setlength{\parskip}{4pt}
\setlist{nosep,leftmargin=0.24in}
\titlespacing*{\section}{0pt}{0.35em}{0.1em}
\titlespacing*{\subsection}{0pt}{0.25em}{0.08em}
\titleformat{\section}{\normalfont\bfseries\large}{}{0pt}{}
\titleformat{\subsection}{\normalfont\bfseries}{}{0pt}{}

\begin{document}
\begin{center}
{\Large\bfseries References Cited}\\[0.05in]
{\normalsize Mostafa Rezaali}\\
{\normalsize NSF AGS-PRF Application}
\end{center}
\vspace{-0.08in}
\noindent Lam, R., Sanchez-Gonzalez, A., Willson, M., Wirnsberger, P., Fortunato, M., Alet, F., Ravuri, S., Ewalds, T., Eaton-Rosen, Z., Hu, W., Merose, A., Hoyer, S., Holland, G., Vinyals, O., Stott, J., Pritzel, A., Mohamed, S., and Battaglia, P. (2023). Learning skillful medium-range global weather forecasting. \textit{Science}, 382(6677), 1416--1421.

\noindent Price, I., Sanchez-Gonzalez, A., Alet, F., Andersson, T. R., El-Kadi, A., Masters, D., Ewalds, T., Stott, J., Mohamed, S., Battaglia, P., Lam, R., and Willson, M. (2024). Probabilistic weather forecasting with machine learning. \textit{Nature}, 637, 84--90.

\noindent Pegion, K., Kirtman, B. P., Becker, E., Collins, D. C., LaJoie, E., Burgman, R., Bell, R., DelSole, T., Min, D., Zhu, Y., Li, W., Sinsky, E., Guan, H., Gottschalck, J., Metzger, E. J., Barton, N. P., Achuthavarier, D., Marshak, J., Koster, R., Lin, H., Gagnon, N., Bell, M., Tippett, M. K., Robertson, A. W., Sun, S., Benjamin, S. G., Green, B. W., Bleck, R., and Kim, H. (2019). The Subseasonal Experiment SubX: A multimodel subseasonal prediction experiment. \textit{Bulletin of the American Meteorological Society}, 100(10), 2043--2060.

\noindent Vitart, F., Ardilouze, C., Bonet, A., Brookshaw, A., Chen, M., Codorean, C., Deque, M., Ferranti, L., Fucile, E., Fuentes, M., Hendon, H., Hodgson, J., Kang, H. S., Kumar, A., Lin, H., Liu, G., Liu, X., Malguzzi, P., Mallas, I., Manoussakis, M., Mastrangelo, D., MacLachlan, C., McLean, P., Minami, A., Mladek, R., Nakazawa, T., Najm, S., Nie, Y., Rixen, M., Robertson, A. W., Ruti, P., Sun, C., Takaya, Y., Tolstykh, M., Venuti, F., Waliser, D., Woolnough, S., Wu, T., Won, D. J., Xiao, H., Zaripov, R., and Zhang, L. (2017). The Sub-seasonal to Seasonal Prediction Project Database. \textit{Bulletin of the American Meteorological Society}, 98(1), 163--173.

\noindent White, C. J., Carlsen, H., Robertson, A. W., Klein, R. J. T., Lazo, J. K., Kumar, A., Vitart, F., Coughlan de Perez, E., Ray, A. J., Murray, V., Bharwani, S., MacLeod, D., James, R., Fleming, L., Morse, A. P., Eggen, B., Graham, R., Kjellstrom, E., Becker, E., Pegion, K. V., Holbrook, N. J., McEvoy, D., Depledge, M., Perkins-Kirkpatrick, S., Brown, T. J., Street, R., Jones, L., Remenyi, T. A., Hodgson-Johnston, I., Buontempo, C., Lamb, R., Meinke, H., Arheimer, B., and Zebiak, S. E. (2017). Potential applications of subseasonal-to-seasonal predictions. \textit{Meteorological Applications}, 24(3), 315--325.

\noindent Otkin, J. A., Anderson, M. C., Hain, C., Svoboda, M., Johnson, D., Mueller, R., Tadesse, T., Wardlow, B., and Brown, J. (2016). Assessing the evolution of soil moisture and vegetation conditions during the 2012 United States flash drought. \textit{Agricultural and Forest Meteorology}, 218--219, 230--242.

\noindent Rasp, S., Dueben, P. D., Scher, S., Weyn, J. A., Mouatadid, S., and Thuerey, N. (2020). WeatherBench: A benchmark data set for data-driven weather forecasting. \textit{Journal of Advances in Modeling Earth Systems}, 12, e2020MS002203.

\noindent Rezaali, M., Jahangir, M. S., Fouladi-Fard, R., and Keellings, D. (2024). An ensemble deep learning approach to spatiotemporal tropospheric ozone forecasting: A case study of Tehran, Iran. \textit{Urban Climate}, 55, 101950.

\noindent Rezaali, M., Quilty, J., and Karimi, A. (2021). Probabilistic urban water demand forecasting using wavelet-based machine learning models. \textit{Journal of Hydrology}, 600, 126358.
\end{document}
