\documentclass[11pt,letterpaper]{article}

% ======= PACKAGES =======
\usepackage[utf8]{inputenc}
\usepackage{geometry}
\geometry{margin=1in}
\usepackage{setspace}
\setstretch{1.5}
\usepackage{fancyhdr}
\usepackage{xcolor}
\usepackage{titlesec}
\usepackage{lastpage}
\usepackage{hyperref}
\usepackage{mathpazo}
\usepackage{graphicx}
\usepackage{subcaption}
\linespread{1.5}

% ======= HEADER & FOOTER =======
\pagestyle{fancy}
\fancyhf{}

% Header (faded + smaller)
\fancyhead[L]{\footnotesize\textcolor{gray!90}{\textit{Collaborators and Other Affiliations}}}
\fancyhead[R]{\footnotesize\textcolor{gray!90}{\textit{Mostafa Rezaali}}}

% Footer (faded)
\fancyfoot[L]{\footnotesize\textcolor{gray!90}{\textit{NSF AGS-PRF -- University of Florida}}}
\fancyfoot[R]{\footnotesize\textcolor{gray!90}{Page \thepage}}

\renewcommand{\headrulewidth}{0.4pt}
\renewcommand{\footrulewidth}{0.4pt}

% ======= PARAGRAPH STYLE =======
\setlength{\parindent}{15pt}
\setlength{\parskip}{6pt}
\titlespacing*{\section}{0pt}{0.55em}{0.2em}
\titlespacing*{\subsection}{0pt}{0.45em}{0.15em}

% ======= DOCUMENT BEGINS =======
\begin{document}

% ======= TITLE BLOCK =======
\begin{center}
    \vspace*{-1.5cm}
    {\Large\bfseries Postdoctoral Fellowship Application} \\[0.2cm]
    {\small\textit{NSF Atmospheric and Geospace Sciences Postdoctoral Research Fellowship}} \\[0.05cm]
    {\small\textit{Department of Geography, University of Florida}} \\[0.1cm]
    \rule{0.6\textwidth}{0.4pt}
\end{center}
\vspace{-0.5cm}

\noindent
Mostafa Rezaali \\
Ph.D. Candidate, Climate Science (Geography) \\
University of Florida \\
\href{mailto:mostafarezaali@gmail.com}{mostafarezaali@gmail.com} \quad $\mid$ \quad (352) 709-5350 \\[0.3cm]
{\large\bfseries Collaborators and Other Affiliations}\\[-0.15cm]
\rule{\textwidth}{0.4pt}
\section*{Graduate, Postdoctoral, and Thesis Advisors}
\begin{itemize}
\item David Keellings, University of Florida.
\item Ali Karimi, Qom University of Technology.
\end{itemize}

\section*{Principal Collaborators and Co-Authors}
The following individuals are known collaborators or co-authors from the application materials and CV:
\begin{itemize}
\item A. Narayanan, E. L. Bunting, and David Keellings.
\item R. Fouladi-Fard, A. Karimi, M. S. Jahangir, J. Quilty, H. Mojarad, A. Sorooshian, M. Mahdinia, P. O'Shaughnessy, K. Naddafi.
\item M. Farajollahi, M. Fahiminia, N. R. Rahimi, R. Aali, Shahryari, N. Moghadam Yekta, B. Mohammadnezhad, A. Rasouli.
\end{itemize}

\section*{Institutional Affiliations}
\begin{itemize}
\item University of Florida, Gainesville, Florida, United States.
\item Qom University of Technology, Qom, Iran.
\item IAUKHSH, Isfahan, Iran.
\end{itemize}

\section*{Disclosure Note}
This PDF is a readable companion summary prepared from the CV and application materials available locally. NSF normally requires the Collaborators and Other Affiliations information to be prepared using the NSF COA spreadsheet template and uploaded as the Research.gov single-copy COA document. Before final submission, the official COA template should be reviewed to ensure all categories, dates, co-authors within the required lookback window, collaborators, and organizational affiliations are complete.

\end{document}
